Comparison to Christensen et al. 2018

### 2019-07-10 doc/paper-comparison.Rmd

ldats_ldats_cpt <- TS_on_LDA(LDA_models = ldats_lda_selected,
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             weights = NULL,
                             control = TS_controls_list(timename = 'newmoon'))

@@

paper_ldats_cpt <- TS_on_LDA(LDA_models = ldamodel,
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             weights = NULL,
                              control = TS_controls_list(timename = 'newmoon'))

>>>>

ldats_ldats_cpt <- TS_on_LDA(LDA_models = ldats_lda_selected,
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             timename = 'newmoon',
                             weights = NULL)

@@

paper_ldats_cpt <- TS_on_LDA(LDA_models = ldamodel,
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             timename = 'newmoon',
                             weights = NULL)
